% !TEX root = graph.tex

\documentclass[twocolumn]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{CJKutf8}
% \usepackage{amsthm}
\usepackage{mdframed}
\usepackage{multicol} % 用於分欄
\usepackage{geometry} % 用於調整頁面尺寸和邊距
\usepackage{amsmath}
\usepackage{titlesec}

\newtheorem{example}{example}             % 整体编号
\newtheorem{algorithm}{algorithm}
\newtheorem{theorem}{theorem}[section]  % 按 section 编号
\newtheorem{definition}{definition}
\newtheorem{axiom}{axiom}
\newtheorem{property}{property}
\newtheorem{proposition}{proposition}
\newtheorem{lemma}{lemma}
\newtheorem{corollary}{corollary}
\newtheorem{remark}{remark}
\newtheorem{condition}{condition}
\newtheorem{conclusion}{conclusion}
\newtheorem{assumption}{assumption}
\newtheorem{formula}{formula}
\newtheorem{problem}{problem}
\newtheorem{solution}{solution}

\linespread{0.5}
% \setlength{\parskip}{0.001em}

\setlength{\topsep}{0.1em} % 環境之上和之下的距離
\setlength{\partopsep}{0pt} % 環境和上下文之間的額外距離
\setlength{\itemsep}{0.5em} % 項目之間的距離
\setlength{\parsep}{0pt} % 段落之間的距離

\titlespacing*{\section}{0pt}{0pt}{0pt}

% 設定頁面尺寸和邊距
\geometry{
    top=0.5cm,
    bottom=0.5cm,
    left=0.5cm,
    right=0.5cm
}


% 自定義 "Definition" 環境
% \newmdtheoremenv{definition}{Definition}
% \theoremstyle{mystyle}

\title{}
% \author{}
% \date{}

\begin{document}
\begin{CJK*}{UTF8}{bkai}

% \maketitle

% 第一部分（Chapter 1）
\section{Fundamentals}

    % \switchcolumn[0]
    % 左欄內容
    % \newtheorem{definition}{def}
    \begin{definition}
        The degree of vertex u, denoted deg(u), is the number of edges that are
 incident to u, except that each loop at u counts twice.
    \end{definition}

    \begin{definition}
    The size of G is the number of its edges, usually denoted as e(G) or |E(G)|.
    \end{definition}
    
    \begin{definition}
        The order of a graph G is the number of its vertices, usually denoted as n,
 n(G), or |V (G)|.
    \end{definition}
    
    \begin{formula}
    \[
    \sum_{v \in V(G)} \deg(v) = 2 |E(G)|
    \]
    \end{formula}

    \begin{definition}
        A complete graph Kn is a graph of order n s.t. every pair of vertices are
 adjacent.
    \end{definition}

    \begin{definition}
        A path Pn is a graph s.t. V(Pn) = {v1,v2,...,vn} and
 E(Pn) = $\{v_{1}v_{2},v_{2}v_{3},...,v_{n−2}v_{n−1},v_{n−1}v_{n}\}$
    \end{definition}

    \begin{definition}
        A cycle Cn is a graph obtained from Pn by adding edge vn v1.
    \end{definition}

    \begin{definition}
     A graph H is a subgraph of G if H can be obtained from G by deleting any
 number of vertices (and their incident edges) and any number of remaining
 edges. We say G contains H, H $\subseteq$ G, or just G has H.        
    \end{definition}
    
    \begin{definition}
        Let T $\subseteq$ V(G). A graph H is a induced subgraph of G if H can be obtained
 from G by deleting all vertices not in T. We write H = G[T], or H is the
 subgraph of G induced by T.       
    \end{definition}

    \begin{definition}
         Intuitively if graphs G and H are equivalent except for names, we say G is
 isomorphic to H, there is an isomorphism from H to G, or G and H are
 isomorphic. We denote it as G $\cong$ H
    \end{definition}

    \begin{theorem}{(Konig's Theorem on bipartite graphs)}
        A graph G is bipartite $\iff$ it has no odd cycle.
    \end{theorem}

    \begin{definition}
        A walk is a list v0,e1,v1,e2,v2,...,ek,vk of vertices and edges s.t. for each
 1 $\leq$i$\leq$k, the edge ei has endpoints vi−1 and vi.
    \end{definition}

    \begin{definition}
        A trail is a walk without repeated edges.
    \end{definition}

    \begin{definition}
         A path is a trail without repeated vertices.
    \end{definition}

    \begin{definition}
         A u,v-walk, u,v-trail, or u,v-path is a walk, trail, or path that starts and ends
 at vertices u and v, respectively. u can be identical to v. The length of a walk
 is the number of edges it contains.
    \end{definition}

    \begin{lemma}
        A walk W is a path $\iff$ it does not have repeated vertices.
    \end{lemma}

    % \switchcolumn

    \begin{lemma}
        Every u,v-walk W contains a u,v-path.
    \end{lemma}

    \begin{definition}
         A graph G is connected if it has a u,v-path(walk) for every u,v $\in$ V(G).
 Otherwise it is disconnected. If G has a u,v-path(walk) then u is connected to
 v.
    \end{definition}

    \begin{definition}
        The connection relation between vertices is transitive, reflexive, and
 symmetric. So it is an equivalence relation and defines equivalence classes,
 which we call connected components.
    \end{definition}

    \begin{lemma}
         Every graph with n vertices and k edges has at least n −k components, i.e.
 $e(G) +c(G) \geq n(G)$.
    \end{lemma}

    \begin{definition}
         c(G) = number of components in G
    \end{definition}

    \begin{lemma}
         Every closed odd walk W contains an odd cycle.
    \end{lemma}

    \begin{definition}
        A graph is Eulerian if it has a closed trail containing all edges. We call a
 closed trail a circuit if we do not specify the first vertex but keep the list in
 cyclic order. An Eulerian circuit or Eulerian trail is a circuit or trail
 containing all the edges.
    \end{definition}

    \begin{definition}
        An even graph is a graph with vertex degrees all even. A vertex is odd/even
 when its degree is odd/even.
    \end{definition}

    \begin{lemma}
        If every vertex of a graph G has a degree at least 2, then G contains a cycle.
    \end{lemma}

    \begin{definition}
         A component or graph is trivial if it has no edges; otherwise it is nontrivial.
 An isolated vertex is a vertex of degree 0.
    \end{definition}

    \begin{theorem}{(Euler's Theorem)}
        A graph G is Eulerian $\iff$ it has at most one nontrivial component and its
 vertices all have even degree.
    \end{theorem}
    
    \begin{definition}
        A decomposition of a graph is a list of subgraphs s.t. every edge appears in
 exactly one subgraph in the list.
    \end{definition}

    \begin{definition}
        A tournament is a digraph where there is an edge between every pair of
 vertices.
    \end{definition}

    \begin{definition}
         A king in a digraph is a vertex from which every vertex is reachable by a path
 of length at most 2.
    \end{definition}

    \begin{proposition}
        Every tournament has a king.
    \end{proposition}

    \begin{definition}
         A sequence d = (d1,d2,...,dn) is graphic if it is the degree sequence of some
 simple graph.
    \end{definition}

    \begin{theorem}{(Havel-Hakimi)}
         For n >1, an integer list d of size n is graphic $\iff$ $d\prime$ is graphic, where $d\prime$ is
 obtained from d by deleting its largest element $\Delta$ and subtracting 1 from its $\Delta$
 next largest elements. The only 1-element graphic sequence is d = (0).
    \end{theorem}

    \begin{definition}
         A cut-edge or cut-vertex of a graph is an edge or vertex whose deletion
 increases the number of components.
    \end{definition}

    \begin{theorem}
        An edge e is a cut-edge $\iff$ it belongs to no cycle.
    \end{theorem}

    % 右欄內容
    
    

% \vspace{2cm} % 分隔不同章節

% 第二部分（Chapter 2）
\section{Tree}
% \begin{multicol}{2} % 第二部分分欄
    % \switchcolumn[0]

    \begin{theorem}{(Cayley's Formula,)}
         For a set S $\subseteq$ N of size n, there are $n^{n-2}$ trees with vertex set S.
    \end{theorem}

    \begin{lemma}
        Vertex v is a leaf of a tree T $\iff$ v is missing in $T's$ Prufer code f(T).
    \end{lemma}

    \begin{lemma}
        Let S $\subseteq$ N and n=|S|. Prufer algorithm f : \{trees with vertex set S\} → $S^{n-2}$
 is a bijection and thus Cayley's Formula holds.
    \end{lemma}    

    \begin{definition}
         $\tau$(G): the number of spanning trees of connected graph G
    \end{definition}

    \begin{definition}
        M(x|y) is the matrix obtained from M by deleting row (set) x and deleting
 column (set) y.

 M(x|y] is the matrix obtained from M by deleting row (set) x and keeping
 column (set) y.

 M[x|y) is the matrix obtained from M by keeping row (set) x and deleting
 column (set) y.

 M[x|y] is the matrix obtained from M by keeping row (set) x and keeping
 column (set) y.

 [•| means keeping all rows
 
 |•] means keeping all columns
    \end{definition}

    % \switchcolumn

    \begin{theorem}{(Matrix Tree theorem)}
        Given a loopless graph G with vertex set v1,...,vn, let ai,j be the number of
 edges with endpoints vi and vj. Let L be the matrix in which Li,j is -ai,j if
 i $\neq$ j and is deg(vi) when i = j. Then
 $\tau(G) = (-1)^{s+t}detL(s|t)$
 for any row s and any column t.
    \end{theorem}

    \begin{lemma}{(Binet-Cauchy Formula)}
        Let \( C_{n \times n} = A_{n \times m} B_{m \times n} \). Then
        \[
        \det C = \sum_{S \in \binom{[m]}{n}} \det A[\bullet |S] \det B[S| \bullet]
        \]

        where $\binom{[m]}{n}$ denote the set of all n-element subsets of [m].
    \end{lemma}

    \begin{theorem}{(MST-preservingTheorem)}
        Let G =(V,E) be a connected graph and w : E(G) → R be a weight function.
 Let A $\subset$E(G) be contained in some minimum spanning tree for G, let
 [S, V -S] be a cut s.t. no edge in A crosses [S,V -S]. Suppose that uv is a
 cheapest edge crossing [S,V - S] , then A $\cup$ \{uv\} is contained in some
 minimum spanning tree for G.
    \end{theorem}

    \begin{definition}
         A minimum connected spanning subgraph (MCSS) of a weighted connected
 graph G is a connected spanning subgraph with minimum total edge weight.
    \end{definition}

    \begin{lemma}
        If all edge weights of a connected graph G are positive, then MCSS of G is
 equivalent to MST of G.
    \end{lemma}

    \begin{lemma}
        If all edge weights of a connected graph G are nonnegative, then every MCSS
 of G contains an MST of G.
    \end{lemma}

    \begin{lemma}
         Every MCSS of G contains all edges with negative weight.
    \end{lemma}
    % 左欄內容
    % \begin{definition}
    %     這是第二章左欄的定義示例。
    % \end{definition}
    % 這是第二章的左欄內容示例。

    % \switchcolumn
    % % 右欄內容
    % 這是第二章的右欄內容示例。
    % \begin{definition}
    %     這是第二章右欄的另一個定義示例。
    % \end{definition}
% \end{multicol}
% \vspace{2cm} % 分隔不同章節

% 第三部分（Chapter 3）
\section{Matching and factor}
    \begin{definition}
        A matching in a graph G is a set of non-loop edges with no shared endpoints.
 The vertices incident to the edges of a matching M are saturated by M or
 M-saturated; the others are M-unsaturated. A perfect matching in a graph is
 a matching that saturates every vertex. The size of a matching is the number
 of edges in it.
    \end{definition}

    \begin{definition}
        A maximal matching in a graph is a matching that cannot be enlarged by
 adding an edge. A maximum matching is a matching of maximum size among
 all matchings in a graph.
    \end{definition}

    \begin{definition}
        Given a matching M, an M-alternating path is a path that alternates between
 edges in M and edges not in M. An M-alternating path whose endpoints are
 unsaturated by M is an M-augmenting path.
    \end{definition}

    \begin{definition}
        Given two matching M,M', the symmetric difference of M,M' is
 (M -M') $\cup$(M'-M), i.e., the edges in M but not M' and the edges in M'
 but not M.
    \end{definition}

    \begin{lemma}
        Every (nontrivial) component of the symmetric difference of two matchings
 M,M' is a path or an even cycle.
    \end{lemma}

    \begin{theorem}{(Berge)}
        A matching M in a graph G is maximum $\iff$ G has no M-augmenting path.
    \end{theorem}

    \begin{theorem}{ (Hall's Theorem, P. Hall 1935)}
         An X,Y-bigraph G has a matching that saturates X $\iff$ |N(S)| $\geq$ |S| for all
 S $\subseteq$ X.
    \end{theorem}

    \begin{corollary}{(Marriage Theorem)}
        An X,Y-bigraph G, where |X| = |Y|, has a perfect matching $\iff$ |N(S)| $\geq$ |S|
 for all S $\subseteq$ X.
    \end{corollary}

    \begin{definition}
        System of Distinct Representatives (SDR)
 There are n clubs in XXX University. An SDR is a set of distinct club
 representatives, one for each club.
    \end{definition}

    \begin{theorem}
        An SDR exists $\iff$ for every set S of clubs, the size of the unions of their
 members is at least |S|.
    \end{theorem}

    \begin{definition}
        An n$\times$n 0-1 matrix A does not contain an n$\times$n permutation matrix $\iff$ A
 has an r $\times$s all-zeros submatrix with r +s > n.
    \end{definition}

    \begin{corollary}
         For k > 0, every k-regular bipartite graph has a perfect matching.
    \end{corollary}

    \begin{definition}
         A decomposition of a graph is a list of subgraphs s.t. every edge appears in
 exactly one subgraph in the list.
    \end{definition}

    \begin{corollary}
        A k-regular bipartite graph G can be decomposed into k perfect matchings.
    \end{corollary}

    \begin{definition}
        A vertex cover of a graph G is a set Q $\subseteq$ V(G) that contains at least one
 endpoint of every edge. The vertices in Q cover E(G).
 Trivially, V (G) is a vertex cover of G. The minimum cardinality of a vertex
 cover of G is denoted by $\beta(G)$.
    \end{definition}

    \begin{definition}
        $\alpha$(G): maximum size of independent set

 $\alpha$'(G): maximum size of matching
 $\beta$(G): minimum size of vertex cover
 $\beta$'(G): minimum size of edge cover
    \end{definition}

    \begin{lemma}
        In a graph G, S $\subseteq$ V(G) is an independent set $\iff$ V(G)-S is a vertex cover,
 and hence $\alpha$(G)+$\beta$(G) = n(G).
    \end{lemma}

    \begin{theorem}{(Konig 1931, Egervary 1931)}
        If G is a bipartite graph, then the maximum size of a matching in G is equal
 to the minimum size of a vertex cover of G, i.e., $\alpha$'(G) = $\beta$(G).
    \end{theorem}

    \begin{corollary}
         If we find a matching and a vertex cover, both of size k, in bipartite graph G,
 then $\alpha$'(G) = $\beta$(G) = k.
    \end{corollary}

    \begin{definition}
        An edge cover of G is a set L of edges s.t. every vertex of G is incident to
 some edge of L.
 The minimum size of edge cover of G is denoted by $\beta$'(G).
    \end{definition}

    \begin{theorem}{(Gallai 1959)}
        If G is a graph without isolated vertices, then $\alpha$'(G) + $\beta$'(G) = n(G), i.e., the
 maximum size of matching and the minimum size of edge cover sum up to the
 order of G.
    \end{theorem}

    \begin{corollary}{(Konig 1916)}
        If G is a bipartite graph with no isolated vertices, then $\alpha$(G) = $\beta$'(G), i.e., the
 size of maximum independent set is equal to the size of minimum edge cover.
    \end{corollary}

    \begin{corollary}
        If we find an independent set and an edge cover, both of size k, in bipartite
 graph G without isolated vertices, then $\alpha$(G) = $\beta$'(G) = k.
    \end{corollary}

    \begin{definition}
        A factor of a graph G is a spanning subgraph of G, i.e., with vertex set V (G).
 A k-factor is a spanning k-regular subgraph. An odd component of a graph is
 a component of odd order; the number of odd component of G is denoted o(G).

 1-factor are almost same as perfect matching:

 1-factor: subgraph
 
 perfect matching: set of edges
    \end{definition}

\section{HW}
\subsection{hw1}
    \begin{problem}
 Prove that no bipartite graph contains an odd cycle    
    \end{problem}
    
    \begin{solution}
    Suppose that A, B-bigraph G contains an odd cycle C = (v1, v2, . . . , v 2k+1). Without loss of generality suppose that v1 $\in$ A. Since G is bipartite and v1 v2 $\in$ E(G), v2 $\in$ B. Similarly, v2 v3 $\in$ E(G)
and thus v3 $\in$ A, and so on. So v2k+1 $\in$ A. However v1 v2k+1 $\in$ E(G) and yet v1, v 2k+1 $\in$ A, a
contradiction to the hypothesis that G is an A, B-bigraph.

    \end{solution}
    
\subsection{hw2}
    \begin{problem}
        Given a simple graph G, $\bar{G}$ is the simple graph with vertex set V(G) such that for any distinct
 vertices u,v $\in$ V (G), u,v are adjacent in $\bar{G}$ if and only if u,v are not adjacent in G.
 Prove that at least one of G and $\bar{G}$ is connected.
    \end{problem}

    \begin{solution}
        If G is connected then we are done, so suppose that G is disconnected and has multiple components.
We aim to prove that any pair of vertices x, y are connected in $\bar{G}$. If x, y belong to different
components in G, then xy $\notin$ E(G) and xy $\in$ E($\bar{G}$). If x, y belong to the same component C in G,
then fix a vertex v in a different component in G. Both x, y are adjacent to v in $\bar{G}$, thus x, y are
connected in $\bar{G}$.

    \end{solution}

\subsection{hw3}

\subsection{hw4}

\subsection{hw5}

\subsection{hw6}

\end{CJK*}
\end{document}
